---
title: "p8105_hw1_ly2565"
author: "Lin Yang"
date: "9/23/2021"
output: github_document
---

# Problem 1

```{r}
library(tidyverse)
```

## Create a data frame

Let's create a data frame.

```{r}
df = tibble(
  norm_samp = rnorm(10),
  norm_samp_pos = norm_samp > 0,
  vec_char = c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine", "ten"),
  vec_factor = factor(c("small", "medium", "large", "large", "small", "large", "medium", "small", "large", "medium"))
)
```

## Find means

Let's try to take the mean of each variable in the dataframe.

```{r, warning = FALSE}
norm_samp_mean = mean(pull(df, norm_samp))
norm_samp_pos_mean = mean(pull(df, norm_samp_pos))
vec_char_mean = mean(pull(df, vec_char))
vec_factor_mean = mean(pull(df, vec_factor))
```

#The mean of random sample is `norm_samp_mean`, the mean of logical vector is `norm_samp_pos_mean`. However, when I try to take the means of character vector and factor vector, it returns that argument is not numeric or logical.

## Convert variables

Let's convert variables using `as.numeric`.

```{r, eval = FALSE}
norm_samp_pos_num = as.numeric(pull(df, norm_samp_pos))
vec_char_num = as.numeric(pull(df, vec_char))
vec_factor_num = as.numeric(pull(df, vec_factor))
```

#The logical vector `norm_samp_pos` is converted to a numeric vector: true to 1, false to 0.

#The factor vecotr `vec_factor` is converted to a numeric vector: large to 1, medium to 2, small to 3. Now, the mean can be calculated.

#The character vector `vec_char` is converted to a numeric vector: result in **NAs introduced by coercion **, the vector is now compsoed only of 10 NAs, and the mean is just NA.







