---
title: "p8105_hw1_ly2565"
author: "Lin Yang"
date: "9/23/2021"
output: github_document
---

# Problem 1

```{r}
library(tidyverse)
```

## Create a data frame

Let's create a data frame.

```{r}
df = tibble(
  norm_samp = rnorm(10),
  norm_samp_pos = norm_samp > 0,
  vec_char = c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine", "ten"),
  vec_factor = factor(c("small", "medium", "large", "large", "small", "large", "medium", "small", "large", "medium"))
)
```

## Find means

Let's try to take the mean of each variable in the dataframe.

```{r, warning = FALSE}
norm_samp_mean = mean(pull(df, norm_samp))
norm_samp_pos_mean = mean(pull(df, norm_samp_pos))
vec_char_mean = mean(pull(df, vec_char))
vec_factor_mean = mean(pull(df, vec_factor))
```

* The mean of random sample is `r norm_samp_mean`.
* The mean of logical vector is `r norm_samp_pos_mean`. 
* However, when I try to take the means of character vector and factor vector, it returns that argument is not numeric or logical.

## Convert variables

Let's convert variables using `as.numeric`.

```{r, eval = FALSE}
norm_samp_pos_num = as.numeric(pull(df, norm_samp_pos))
vec_char_num = as.numeric(pull(df, vec_char))
vec_factor_num = as.numeric(pull(df, vec_factor))
```

* The logical vector *norm_samp_pos* is converted to a numeric vector: true to 1, false to 0.

* The factor vecotr *vec_factor* is converted to a numeric vector: large to 1, medium to 2, small to 3. Now, the mean can be calculated.

* The character vector *vec_char* is converted to a numeric vector: result in **NAs introduced by coercion**, the vector is now compsoed only of 10 NAs, and the mean is just NA.


# Problem 2

## Load the penguins dataset

```{r}
data("penguins", package = "palmerpenguins")
names(penguins)
```

## Describe the penguins dataset

* The names of variables in the dataset are `r names(penguins)`.
* There are `r nrow(penguins)` rows and `r ncol(penguins)` columns in the dataset.
* The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm after removing all missing data in the flipper length column.

## Make a scatterplot and export

```{r, warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("scatterplot_hw1.pdf")
```




